One more attempt on ArXe

### 2015-05-06 structures.tex
add more history of structure determination

@@

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures with 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron:
          \textbf{a)} closest possible \textbf{b)} middle \textbf{c)}
          furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}

>>>>

In the previous studies \cite{Fasshauer13} the ArXe clusters were assumed
to be large and have more than 1500 atoms. The model structures assumed
an fcc structure and not an icosahedral structure as would be more
probable for small clusters.
Additionally,
the expectation value for the number of xenon atoms relies on a pure
xenon gas. Since the xenon content in the mixed gas is much lower, also
the number of xenon atoms can be expected to be by far less. We therefore
start from the estimated number of atoms in the cluster after expansion
of pure argon gas.
We therefore rethink the possible cluster structures.
%Furthermore, the theoretical prediction did not match the experimental results.
%Since the spectra are strongly depending on the cluster structure as shown in
%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
%we rethink the possible cluster structures.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures with 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron:
          \textbf{a)} closest possible \textbf{b)} middle \textbf{c)}
          furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}
